The problem and promise of scale in multilayer networks

### 2020-02-04 paper/manuscript.Rmd
landcover res results

>>>>

Larger landcover resolution scale resulted in decreased proportion of rare and
patchy habitats and low connectivity of individuals in these habitats. In
winter, layer relevance was stable for open and forest habitats but decreased
for forage habitats (Figure 3c). Connective redundancy decreased with increasing
landcover resolution due the decrease in connectivity of individuals in winter
forage habitats, resulting in a multilayer network where neighbours were less
frequently repeated in multiple layers (Figure 3b). Layer similarity was
generally stable for forest and open habitats except for a contrasting increase
in similarity for forest and decrease in similarity for open habitats at 250m
landcover resolution (Figure 3a). Layer similarity was not possible to calculate
between winter and summer forage because, at all landcover resolutions greater
than 10m there were no individuals connected in the network layers. <!--
individuals still used forage but in much lower proportion + lowered opportunity
to associate --> These results indicate the importance of matching landcover
resolution to scale of selection as well as ensuring the landcover product used
has a resolution fine enough to detect relevant landscape features and habitats.
